Shallow EDSLs and Object-Oriented Programming

### 2016-06-28 paper/sections/Conclusion.tex
Conclusion

There are still certain interpretations that can not be modeled modularly,
including transformations and binary methods.
For transformations, we have to refine their return type in extensions and
supply a new implementation by duplicating the original code.
For binary methods like equality, there is no way to refine the argument type.
How to define these methods modularly is a possible line of future work.
Also, it is still tedious to express the inheritance relationships in extensions,
especially when multiple inheritance is used. Another line of future work is to
use some meta-programming mechanisms to eliminate these boilerplate.

>>>>

There are still certain interpretations that can not be modeled modularly using
our approach, including transformations and binary methods.
For transformations, we have to refine their return type in extensions and
supply a new implementation by duplicating the original code.
For binary methods like equality, there is no way to refine the argument type.
Though with advanced type system features of Scala, these can still be defined
modularly~\ref{zenger05independentlyextensible}. However, the encoding would
become complicated.
Also, we can further eliminate some boilerplate through code generation.
For example, similar inheritance relationships are repeated in each constructs
for extensions.
